Unity in diversity: Children from 17 diverse communities process gaze in similar ways

### 2024-02-05 paper/supplement.Rmd
update supplement

---
title: "Unity in diversity: shared basic social-cognitive processing in children from from 17 diverse communities"
subtitle: "Supplementary material"
author: "..."
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\figurename}{Supplementary Figure}
  \renewcommand{\tablename}{Supplementary Table}
---

```{r, echo=FALSE, message=F}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(ggpubr)
library(tidyboot)
library(tidybayes)
library(maps)
library(brms)
library(cowplot)
library(ggridges)
library(papaja)
library(coda)
library(ggrepel)

@@

knitr::opts_chunk$set(echo=F, warning=FALSE, message=FALSE, size="small")

@@

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe", 
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "America",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Zambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)", 
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Türkiye)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)", 
                            uganda = "Nyabyeya (Uganda)"))
```

@@

in the section [site descriptions](#site-descriptions)

@@

knitr::kable(demtab,
             col.names = c("Community", "Country", "Continent", "N", "Sex (male)", "Age (range)"),
             caption = "Participant demographics.", 
             #ote = "Column age shows mean and range in paranthesis.", digits = 2, align = "l"
             )
```

@@

```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community. Left: dots show individual data points. Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))

ggsave(plot = techpred, "../visuals/techpred.png",  height = 7, width = 10, scale = 1)

@@

@@

```{r figpred2, include = T, fig.align = "center", fig.cap = "Household demographics by community.  Vertical lines show individual data points with minimal horizontal jitter to avoid overplotting.", out.width="100%"}

dempred <- data%>%
  group_by(community,continent)%>%
  mutate(older_children = children - 1 - younger_children)%>%
  distinct(subjid, .keep_all = T)%>%
  select(subjid, community, continent, older_children,children, younger_children, household)%>%
  pivot_longer(names_to = "dem", values_to = "value", cols = c(older_children,children, younger_children, household))%>%
  mutate(dem = recode(dem,
                      older_children = "older children",
                            younger_children = "younger children"),
         dem = factor(dem, levels = c("household", "children", "older children", "younger children")))%>%
  ggplot(aes(y = community, x = value))+
  facet_grid(continent~dem, scales = "free", space = "free_y")+
  geom_density_ridges(
    jittered_points = TRUE,
    position = position_points_jitter(width = 0.25, height = 0),
    point_shape = '|',  point_alpha = 1, alpha = 0.7,
  )+
 # geom_density_ridges(
 #    col = "white",
 #    jittered_points = TRUE, quantile_lines = TRUE, scale = 0.9, alpha = 0.7,
 #    vline_size = 1, vline_color = "red",
 #    point_size = 0.4, point_alpha = 1,
 #    position = position_raincloud(adjust_vlines = TRUE)
 #  )
  labs(x = "No. of individuals", y= "")+
  #geom_jitter(alpha = .1, width = 0.1, height = 0.1)+
  theme_few()

ggsave(plot = dempred, "../visuals/dempred.png", height = 8, width = 14, scale = 1.1)

knitr::include_graphics("../visuals/dempred.png")
```

@@

@@

```{r figtask, include = T, fig.align = "center", fig.cap = "Screenshot from the task. The scene depicts the choice phase in a test trial. Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
knitr::include_graphics("../visuals/task.png")
```

@@

We used Bayesian Regression models fit in `R` [] using the package `brms` [@burkner2019bayesian] for all analyses except the cognitive models, which were implemented in the probabilistic programming language `webppl` [@dippl]. For regression models, we used the default priors built in to `brms`. The dependent variable in all regression models was imprecision, that is, the absolute distance between the true location of the balloon (to x-coordinate of its center) and the location where the participant touched the screen. We used a Log-normal distribution to model the data because the natural lower bound for imprecision is zero and the data was right skewed with a long tail to the right. Numeric predictors that entered the models were scaled to have a mean of zero and a standard deviation of 1. For each model we ran four chains with 6000 iterations, removing the first 2000 for burn-in. All models had converging chains (Rhat values < 1.01). Details specific to each analysis can be found below. The analysis code can be found in the online repository associated with the study (link).

@@

`null`:
* `imprecision ~ age + target_centrality + (target_centrality | participant)`

`culture`:
* `imprecision ~ age + target_centrality + (target_centrality | participant) + (target_centrality | culture)`

`culture_age`: 
* `imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | culture)`

```{r}
mdata <- data%>%
  ungroup()%>%
  mutate(ageinyears = as.numeric(scale(ageinyears)),
         targetcentralityx = as.numeric(scale(targetcentralityx)),
         click = abs(clickdistfromtargetcenterx))

@@

```{r}
# draws <- bind_rows(
# as_draws_df(bm_cult_age)%>%
#   select(contains("ageinyears"))%>%
#   select(contains("ageinyears"))%>%
#   select(-contains("sd"))%>%
#   select(-contains("cor"))%>%
#   pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
#   mutate(post = value + b_ageinyears,
#          community = str_remove(community, "r_community"),
#          community = str_remove(community, ",ageinyears]"),
#          community = str_remove(community, "\\["))%>%
#   select(community, post)%>%
#   mutate(type = "ageinyears"),
# 
# as_draws_df(bm_cult_age)%>%
#   select(contains("targetcentralityx"))%>%
#   select(contains("targetcentralityx"))%>%
#   select(-contains("sd"))%>%
#   select(-contains("cor"))%>%
#   select(-contains("subjid"))%>%
#   pivot_longer(cols = contains("targetcentralityx]"), names_to = "community", values_to = "value")%>%
#   mutate(post = value + b_targetcentralityx,
#          community = str_remove(community, "r_community"),
#          community = str_remove(community, ",targetcentralityx]"),
#          community = str_remove(community, "\\["))%>%
#   select(community, post)%>%
#   mutate(type = "targetcentrality")
# )%>%
#   mutate(community = str_replace(community, "\\.", " "),
#          community= str_remove(community,"\\."))
# 
# pdraws <- draws%>%
#   mutate(community = recode(community,
#                             "Auckland (NewZealand)" = "Auckland (New Zealand)",
#                             "BaYaka (Rep.Congo)" = "BaYaka (Rep. Congo)",
#                             "Bandongo (Rep.Congo)" = "Bandongo (Rep. Congo)",
#                             "Buenos Aires(Argentina)" = "Buenos Aires (Argentina)"))%>%
#   left_join(data%>%distinct(community, continent))%>%
#   mutate(continent = factor(continent, levels = c("America", "Africa", "Europe", "Asia", "Oceania"), ordered = T))
# 
# saveRDS(pdraws, "../saves/pdraws.rds")
# 
# post_agg <- pdraws%>%
#   group_by(community, type)%>%
#   summarise(mean = mean(post),
#             lci = hdi_lower(post),
#             uci = hdi_upper(post))
# 
# saveRDS(post_agg, "../saves/post_agg.rds")
```

@@

pdraws <- readRDS("../saves/pdraws.rds")%>%
  mutate(type = recode(type,
                       ageinyears = "Age",
                       targetcentrality = "Target centrality"),
         type = factor(type, levels = c("Age","Target centrality")))

ppred <- ggplot(pdraws, aes(x= post, y = community))+

  geom_density_ridges(col = "white", alpha = .75, fill = "grey")+
  geom_vline(xintercept = 0, lty = 3)+
  facet_grid(continent~type, scales = "free", space = "free_y")+
  #stat_pointinterval(size = 0.1)+
  #xlim(-0.15, 0.1)+
  labs(x = "Posterior model estimate", y= "")+
  theme_few()+
  theme( strip.text.y.right = element_text(angle = 0))

ggsave(plot = ppred, "../visuals/pred.png", height = 6, width = 12, scale = 1)

@@

```{r}
devdata <- data%>%
  mutate(click = abs(clickdistfromtargetcenterx))%>%
  group_by(subjid, continent,community, ageinyears)%>%
  summarise(mean_click = mean(click))%>%
  ungroup()%>%
  mutate(ageinyears = ageinyears - min(ageinyears))

bm_dev <- brm(mean_click ~ ageinyears + (ageinyears |community),
                              data   = devdata,
                              family = lognormal(),
                              warmup = 2000,
                              iter   = 4000,
                              chains = 4,
                              cores  = 4,
             control = list(adapt_delta = 0.95))

ndata <- devdata%>%
  distinct(continent, community, ageinyears)

post <- fitted(bm_dev, newdata = ndata, re_formula =~(ageinyears|community))%>%
  as_tibble() %>%
  bind_cols(ndata)%>%
  mutate(ageinyears = ageinyears + min(data$ageinyears))
```

```{r}
tc_agg_data<- data%>%
  mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
  group_by(continent, community, targetposition)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

tam <- tc_agg_data%>%
  filter(continent == "America")%>%
  ggplot(., aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "", y = "")+
  scale_color_colorblind(name = "", guide = "none")+
  facet_grid(continent~.)+
  ylim(0,1000)+
  theme_few()

taf <- tc_agg_data%>%
  filter(continent == "Africa")%>%
  ggplot(., aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "", y = "")+
  scale_color_colorblind(name = "", guide = "none")+
  facet_grid(continent~.)+
  ylim(0,1000)+
  theme_few()

teu <- tc_agg_data%>%
  filter(continent == "Europe")%>%
  ggplot(., aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "", y = "")+
  scale_color_colorblind(name = "", guide = "none")+
  facet_grid(continent~.)+
  ylim(0,1000)+
  theme_few()

tas <- tc_agg_data%>%
  filter(continent == "Asia")%>%
  ggplot(., aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "", y = "")+
  scale_color_colorblind(name = "", guide = "none")+
  facet_grid(continent~.)+
  ylim(0,1000)+
  theme_few()

toc <- tc_agg_data%>%
  filter(continent == "Oceania")%>%
  ggplot(., aes(x = targetposition, y = mean, col = community))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
  labs(x = "Target position (binned)", y = "")+
  scale_color_colorblind(name = "", guide = "none")+
  facet_grid(continent~.)+
  ylim(0,1000)+
  theme_few()

@@

```{r}
am <- ggplot()+
  geom_point(data = devdata%>%filter(continent == "America"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "America"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="Imprecision")+
  scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

af <- ggplot()+
  geom_point(data = devdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

eu <- ggplot()+
  geom_point(data = devdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

as <- ggplot()+
  geom_point(data = devdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))

oc <- ggplot()+
  geom_point(data = devdata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
  geom_smooth(data = post%>%filter(continent == "Oceania"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
  theme_few()+
  scale_fill_colorblind(name = "")+
  scale_color_colorblind(name = "")+
  labs(x = "Age", y="")+
    scale_x_continuous(limits = c(2,10))+
  scale_y_continuous(limits = c(0,1000))+
  facet_grid(continent~.)+
  theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
```

```{r figdev, include = T, fig.align = "center", fig.cap = "A) Developmental trajectories by cultural settings. Transparent dots show aggregated data for each individual. The color dentoes the different cultural settings. The developmental trajectories are predicted based on a model of the data aggregated for each participant. B) Performance by screen section and cultural setting. Each bin covers 1/10th of the screen. Points show means and eroor bars 95\\% confidence intervals for the data within that bin aggregated across participants.", out.width="100%"}
# plot_grid(
#   plot_grid(am, tam, nrow = 1, align = "h", rel_widths = c(2,1)),
#   plot_grid(af, taf, nrow = 1, align = "h", rel_widths = c(2,1)),
#   plot_grid(eu, teu, nrow = 1, align = "h", rel_widths = c(2,1)),
#   plot_grid(as, tas, nrow = 1, align = "h", rel_widths = c(2,1)),
#   plot_grid(oc, toc, nrow = 1, align = "h", rel_widths = c(2,1)),
#   align = "v",
#   ncol = 1
#   )

>>>>

---
title: "Unity in diversity: Children from 17 diverse communities process gaze in similar ways"
subtitle: "Supplemental material"
author: "..."
output: 
  bookdown::pdf_document2:
    toc: yes 
    number_sections: false    
  bookdown::html_document2:
    toc: yes
    toc_float: true
    fig_caption: yes
    #code_folding: hide
    number_sections: false
bibliography: library.bib
#csl: pnas.csl
header-includes:
  \usepackage{caption}
  \renewcommand{\figurename}{Supplementary Figure}
  \renewcommand{\tablename}{Supplementary Table}
---

```{r, echo=FALSE, message=F}
library(tidyverse)
library(ggpubr)
library(ggthemes)
library(ggpubr)
library(tidyboot)
library(tidybayes)
library(maps)
library(brms)
library(cowplot)
library(ggridges)
library(papaja)
library(coda)
library(ggrepel)
library(knitr)
library(kableExtra)

@@

knitr::opts_chunk$set(echo=F, warning=FALSE, message=FALSE, size="small")
options(knitr.kable.NA = '')

@@

```{r}
data <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(continent = ifelse(
    community %in% c("leipzig", "plymouth"), "Europe",
    ifelse(
      community %in% c("akure", "hai||om", "khwe", "chimfunshi", "bandongo", "bayaka", "windhoek", "uganda"), "Africa",
      ifelse(community %in% c("stanford", "mexico", "buenos_aires"), "Americas",
             ifelse(community %in% c("india", "beijing", "turkey"), "Asia", "Oceania"))
    )
  ))%>%
  mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T))%>%
  mutate(community = recode(community,
                            akure = "Akure (Nigeria)",
                            leipzig = "Leipzig (Germany)",
                            `hai||om` = "Hai||om (Namibia)",
                            khwe = "Khwe (Namibia)",
                            windhoek = "Windhoek (Namibia)",
                            stanford = "Stanford (USA)",
                            chimfunshi = "Chimfunshi (Zambia)",
                            mexico = "Ocuilan (Mexico)",
                            plymouth = "Plymouth (UK)",
                            beijing = "Beijing (China)",
                            india = "Pune (India)",
                            buenos_aires = "Buenos Aires (Argentina)",
                            auckland = "Auckland (New Zealand)",
                            turkey = "Malatya (Türkiye)",
                            bandongo = "Bandongo (Rep. Congo)",
                            bayaka = "BaYaka (Rep. Congo)",
                            uganda = "Nyabyeya (Uganda)"))
```

@@

This docuemnt provides a detailed overview of the participants and methods of the in the section [site descriptions](#site-descriptions)

@@

kableExtra::kable(demtab,
             col.names = c("Community", "Country", "Continent", "N", "Sex (male)", "Age (range)"),
              caption = "Participant demographics.", 
             format="latex", booktabs=TRUE
             )
```

@@

@@

```{r figpred1, include = T, fig.align = "center", fig.cap = "A) Age distribution and B) prevalence of different types of technology by community. Left: dots show individual data points. Right: color shows the proportion of children with access to screens or touchscreens.", out.width="100%"}
# techpred <- plot_grid(page, ppred, rel_widths = c(1, 0.5),align = "h", labels = c("A", "B"))
# 
# ggsave(plot = techpred, "../visuals/techpred.png",  height = 7, width = 10, scale = 1)

@@

```{r figpred2, include = T, fig.align = "center", fig.cap = "Household demographics by community.  Points show individual data points with minimal vertical and horizontal jitter to avoid overplotting. Red points show means with 95\\% CI.", out.width="100%"}

# dempred <- data%>%
#   group_by(community,continent)%>%
#   distinct(subjid, .keep_all = T)%>%
#   select(subjid, community, continent, children, younger_children, household)%>%
#   pivot_longer(names_to = "dem", values_to = "value", cols = c(children, younger_children, household))%>%
#   mutate(dem = recode(dem,
#                       younger_children = "younger children"),
#          dem = factor(dem, levels = c("household", "children", "younger children")))%>%
#   ggplot(aes(y = value, x = community))+
#   facet_grid(dem~continent, scales = "free", space = "free_x")+
#   geom_jitter(width = 0.2, height = 0.1, alpha = 0.1)+
#   geom_pointrange(data = dempred_agg, aes(ymin = ci_lower, ymax = ci_upper, y = mean), col = "firebrick")+
#   theme_few()+
#   labs(y = "No. of individuals", x= "")+
#   theme(axis.text.x = element_text(angle = 55, vjust = 1, hjust=1))
# 
# ggsave(plot = dempred, "../visuals/dempred.png", height = 6, width = 12, scale = 1)

knitr::include_graphics("../visuals/dempred.png")

@@

```{r task, include = T, fig.align = "center", fig.cap = "Screenshot from the task. The scene depicts the choice phase in a test trial. Participants had to use the gaze of the agent to locate the balloon and click on the hedge where they thought the balloon was.", out.width="80%"}
knitr::include_graphics("../visuals/task.png")
```

@@

@@

We used Bayesian Regression models fit in `R` [@r] using the package `brms` [@burkner2019bayesian] for all analyses except the cognitive models, which were implemented in the probabilistic programming language `webppl` [@dippl]. For regression models, we used the default priors built in to `brms`. The dependent variable in all regression models was imprecision, that is, the absolute distance between the true location of the balloon (to x-coordinate of its center) and the location where the participant touched the screen. We used a Log-normal distribution to model the data because the natural lower bound for imprecision is zero and the data was right skewed with a long tail to the right. Numeric predictors that entered the models were scaled to have a mean of zero and a standard deviation of 1. For each model we ran four chains with 6000 iterations, removing the first 2000 for burn-in. All models had converging chains (Rhat values < 1.01). Details specific to each analysis can be found below. The analysis code can be found in the online repository associated with the study (link).

@@

`null`:

* `imprecision ~ age + target_centrality + (target_centrality | participant)`

`culture`:

* `imprecision ~ age + target_centrality + (target_centrality | participant) + (target_centrality | culture)`

`culture_age`:

* `imprecision ~ age + target_centrality + (target_centrality | participant) + (age + target_centrality | culture)`

```{r}
# mdata <- data%>%
#   ungroup()%>%
#   mutate(ageinyears = as.numeric(scale(ageinyears)),
#          targetcentralityx = as.numeric(scale(targetcentralityx)),
#          click = abs(clickdistfromtargetcenterx))

@@

```{r}
# draws <- bind_rows(
# as_draws_df(bm_cult_age)%>%
#   select(contains("ageinyears"))%>%
#   select(contains("ageinyears"))%>%
#   select(-contains("sd"))%>%
#   select(-contains("cor"))%>%
#   pivot_longer(cols = contains("ageinyears]"), names_to = "community", values_to = "value")%>%
#   mutate(post = value + b_ageinyears,
#          community = str_remove(community, "r_community"),
#          community = str_remove(community, ",ageinyears]"),
#          community = str_remove(community, "\\["))%>%
#   select(community, post)%>%
#   mutate(type = "ageinyears"),
# 
# as_draws_df(bm_cult_age)%>%
#   select(contains("targetcentralityx"))%>%
#   select(contains("targetcentralityx"))%>%
#   select(-contains("sd"))%>%
#   select(-contains("cor"))%>%
#   select(-contains("subjid"))%>%
#   pivot_longer(cols = contains("targetcentralityx]"), names_to = "community", values_to = "value")%>%
#   mutate(post = value + b_targetcentralityx,
#          community = str_remove(community, "r_community"),
#          community = str_remove(community, ",targetcentralityx]"),
#          community = str_remove(community, "\\["))%>%
#   select(community, post)%>%
#   mutate(type = "targetcentrality")
# )%>%
#   mutate(community = str_replace(community, "\\.", " "),
#          community= str_remove(community,"\\."))
# 
# pdraws <- draws%>%
#   mutate(community = recode(community,
#                             "Auckland (NewZealand)" = "Auckland (New Zealand)",
#                             "BaYaka (Rep.Congo)" = "BaYaka (Rep. Congo)",
#                             "Bandongo (Rep.Congo)" = "Bandongo (Rep. Congo)",
#                             "Buenos Aires(Argentina)" = "Buenos Aires (Argentina)"))%>%
#   left_join(data%>%distinct(community, continent))%>%
#   mutate(continent = factor(continent, levels = c("Americas", "Africa", "Europe", "Asia", "Oceania"), ordered = T))
# 
# saveRDS(pdraws, "../saves/pdraws.rds")
# 
# post_agg <- pdraws%>%
#   group_by(community, type)%>%
#   summarise(mean = mean(post),
#             lci = hdi_lower(post),
#             uci = hdi_upper(post))
# 
# saveRDS(post_agg, "../saves/post_agg.rds")
```

@@

# pdraws <- readRDS("../saves/pdraws.rds")%>%
#   mutate(type = recode(type,
#                        ageinyears = "Age",
#                        targetcentrality = "Target centrality"),
#          type = factor(type, levels = c("Age","Target centrality")))
# 
# 
# 
# ppred <- ggplot(pdraws, aes(x= post, y = community))+
# 
#   geom_density_ridges(col = "white", alpha = .75, fill = "grey")+
#   geom_vline(xintercept = 0, lty = 3)+
#   facet_grid(continent~type, scales = "free", space = "free_y")+
#   #stat_pointinterval(size = 0.1)+
#   #xlim(-0.15, 0.1)+
#   labs(x = "Posterior model estimate", y= "")+
#   theme_few()+
#   theme( strip.text.y.right = element_text(angle = 0))
# 
# 
# ggsave(plot = ppred, "../visuals/pred.png", height = 6, width = 12, scale = 1)

@@

```{r}
# devdata <- data%>%
#   mutate(click = abs(clickdistfromtargetcenterx))%>%
#   group_by(subjid, continent,community, ageinyears)%>%
#   summarise(mean_click = mean(click))%>%
#   ungroup()%>%
#   mutate(ageinyears = ageinyears - min(ageinyears))
# 
# bm_dev <- brm(mean_click ~ ageinyears + (ageinyears |community),
#                               data   = devdata,
#                               family = lognormal(),
#                               warmup = 2000,
#                               iter   = 4000,
#                               chains = 4,
#                               cores  = 4,
#              control = list(adapt_delta = 0.95))
# 
# 
# ndata <- devdata%>%
#   distinct(continent, community, ageinyears)
# 
# 
# post <- fitted(bm_dev, newdata = ndata, re_formula =~(ageinyears|community))%>%
#   as_tibble() %>%
#   bind_cols(ndata)%>%
#   mutate(ageinyears = ageinyears + min(data$ageinyears))
```

```{r}
# tc_agg_data<- data%>%
#   mutate(targetposition = factor(targetposition, levels = c(1:10)))%>%
#   group_by(continent, community, targetposition)%>%
#   tidyboot_mean(col= abs(clickdistfromtargetcenterx))
# 
# 
# tam <- tc_agg_data%>%
#   filter(continent == "Americas")%>%
#   ggplot(., aes(x = targetposition, y = mean, col = community))+
#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
#   labs(x = "", y = "")+
#   scale_color_colorblind(name = "", guide = "none")+
#   facet_grid(continent~.)+
#   ylim(0,1000)+
#   theme_few()
# 
# taf <- tc_agg_data%>%
#   filter(continent == "Africa")%>%
#   ggplot(., aes(x = targetposition, y = mean, col = community))+
#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
#   labs(x = "", y = "")+
#   scale_color_colorblind(name = "", guide = "none")+
#   facet_grid(continent~.)+
#   ylim(0,1000)+
#   theme_few()
# 
# teu <- tc_agg_data%>%
#   filter(continent == "Europe")%>%
#   ggplot(., aes(x = targetposition, y = mean, col = community))+
#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
#   labs(x = "", y = "")+
#   scale_color_colorblind(name = "", guide = "none")+
#   facet_grid(continent~.)+
#   ylim(0,1000)+
#   theme_few()
# 
# tas <- tc_agg_data%>%
#   filter(continent == "Asia")%>%
#   ggplot(., aes(x = targetposition, y = mean, col = community))+
#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
#   labs(x = "", y = "")+
#   scale_color_colorblind(name = "", guide = "none")+
#   facet_grid(continent~.)+
#   ylim(0,1000)+
#   theme_few()
# 
# toc <- tc_agg_data%>%
#   filter(continent == "Oceania")%>%
#   ggplot(., aes(x = targetposition, y = mean, col = community))+
#   geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),pch = 1, alpha = 0.75, position = position_dodge(width = .5))+
#   labs(x = "Target position (binned)", y = "")+
#   scale_color_colorblind(name = "", guide = "none")+
#   facet_grid(continent~.)+
#   ylim(0,1000)+
#   theme_few()

@@

```{r}
# am <- ggplot()+
#   geom_point(data = devdata%>%filter(continent == "Americas"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
#   geom_smooth(data = post%>%filter(continent == "Americas"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
#   theme_few()+
#   scale_fill_colorblind(name = "")+
#   scale_color_colorblind(name = "")+
#   labs(x = "", y="Imprecision")+
#   scale_x_continuous(limits = c(2,10))+
#   scale_y_continuous(limits = c(0,1000))+
#   facet_grid(continent~.)+
#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
# 
# af <- ggplot()+
#   geom_point(data = devdata%>%filter(continent == "Africa"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
#   geom_smooth(data = post%>%filter(continent == "Africa"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
#   theme_few()+
#   scale_fill_colorblind(name = "")+
#   scale_color_colorblind(name = "")+
#   labs(x = "", y="")+
#     scale_x_continuous(limits = c(2,10))+
#   scale_y_continuous(limits = c(0,1000))+
#   facet_grid(continent~.)+
#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
# 
# eu <- ggplot()+
#   geom_point(data = devdata%>%filter(continent == "Europe"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
#   geom_smooth(data = post%>%filter(continent == "Europe"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
#   theme_few()+
#   scale_fill_colorblind(name = "")+
#   scale_color_colorblind(name = "")+
#   labs(x = "", y="")+
#     scale_x_continuous(limits = c(2,10))+
#   scale_y_continuous(limits = c(0,1000))+
#   facet_grid(continent~.)+
#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
# 
# as <- ggplot()+
#   geom_point(data = devdata%>%filter(continent == "Asia"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
#   geom_smooth(data = post%>%filter(continent == "Asia"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
#   theme_few()+
#   scale_fill_colorblind(name = "")+
#   scale_color_colorblind(name = "")+
#   labs(x = "", y="")+
#     scale_x_continuous(limits = c(2,10))+
#   scale_y_continuous(limits = c(0,1000))+
#   facet_grid(continent~.)+
#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
# 
# oc <- ggplot()+
#   geom_point(data = devdata%>%filter(continent == "Oceania"), aes(x = ageinyears+ min(data$ageinyears), y = mean_click, col = community), alpha = 0.25)+
#   geom_smooth(data = post%>%filter(continent == "Oceania"), aes(x = ageinyears, y = Estimate, ymin = Q2.5, ymax = Q97.5, fill =community, col = community), stat = "identity", alpha = .25)+
#   theme_few()+
#   scale_fill_colorblind(name = "")+
#   scale_color_colorblind(name = "")+
#   labs(x = "Age", y="")+
#     scale_x_continuous(limits = c(2,10))+
#   scale_y_continuous(limits = c(0,1000))+
#   facet_grid(continent~.)+
#   theme(strip.text = element_blank(), legend.justification = c(0,1),legend.text=element_text(size=8))
```

```{r figdev, include = T, fig.align = "center", fig.cap = "A) Developmental trajectories by cultural settings. Transparent dots show aggregated data for each individual. The color dentoes the different cultural settings. The developmental trajectories are predicted based on a model of the data aggregated for each participant. B) Performance by screen section and cultural setting. Each bin covers 1/10th of the screen. Points show means and eroor bars 95\\% confidence intervals for the data within that bin aggregated across participants.", out.width="75%"}
